Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-27 docs/manuscript/manuscript.tex
Added body paragraph for introduction for more information on the access we are studying.

%%\item Cite statistics from the WHO/UN on the water situation...
%%\item What has been the rate of improvement over the years?

@@

Improving water accessibility has been a priority by many organizations around the world, realizing it is the basic human right to have clean and accessible drinkable water in the past 15 years. From 2006 to 2016, overall water accessibility has been improving by utilizing the indicators of the past \citep{fullerTrackingProgressGlobal2016}. However, some researchers raise concerns on lack of clarity with the global water accessibility monitoring \citep{ondaGlobalAccessSafe2012, jiaHighResolutionSpatialDistribution2016}. However, in an era of rapidly changing advanced technologies, international, and government policies, some of the older research might not be adequate for up to date information for example of The eight Millennium Development Goals (MDGs) upgrading into The Sustainable Development Goals (SDGs). In light of the newest SDGs of providing clean and accessible drinking water for all by 2030, researchers have devoted their studies to understand water accessibility at global and specific country levels. Several research and studies have focused global water accessibility ,and its progress \citep{sorensonSafeAccessSafe2011,bainAccountingWaterQuality2012,wssccWaterSanitationHygiene2014,  ondaGlobalAccessSafe2012, bartramGlobalMonitoringWater2014, ondaCountryClusteringApplied2014, whoDrinkingwater,fullerTrackingProgressGlobal2016, weiyuyuGlobalPerspectiveDrinkingwater2016, grahamAnalysisWaterCollection2016,overboOnplotDrinkingWater2016}. While there have been studies focusing on the local community in different parts of the country learning about their water accessibility and sanitation initiation \citep{jagalsDoesImprovedAccess2006, geereDomesticWaterCarrying2010, simaWaterFlowsEnergy2013, hoChallengeGlobalWater2014, sakisakaIntroductionCommunityWater2015, jiaHighResolutionSpatialDistribution2016}. Where majority raised concerns about the lack of monitoring sustainable water accessibility measurements for many people and even a few argue for greater focus on many people's access to drinking water sources. Nonetheless, there is a lack of robust study on modes of transportation-related to enhance water accessibility for all people by 2030. 

@@

The journal articles were missing what modes of transportation may enhance water accessibility. Therefore we will be analyzing the impact of transportation modes (usage/ownership) on water accessibility. We will therefore research by statistical analysis in a global scale and pilot in one of the countries to determine if the water accessibility variables predictors can improve the water accessibility for its country.

% citep (for citations fully enclosed in parentheses)
% cite (for citations without any parentheses)
% citet (for citations where the year only is in parentheses)
%\textit{Discuss the who/what/when/where? (You already have this... just need to reorganize or improve structure)}

\eject

>>>>

%%\item Cite statistics from the WHO/UN on the water situation...
%%\item What has been the rate of improvement over the years?
A simple necessity of access is the existence of an actual water source. People can obtain water from nature in a variety of ways, but Sustainable Development Goals (SDGs) has determined the "A safely managed drinking water service" which are proper for human consumption \citep{wssccWaterSanitationHygiene2014,whoDrinkingwater,GoalCleanWater}. A safely managed drinking water service is defined as one located on-premises, available when needed and free from contamination \citep{GoalCleanWater}. This definition requires a basic drinking water source that is positioned on-premises, available when needed, and free of fecal and priority chemical contamination. While basic drinking water sources are described as piped water, boreholes or
tube wells, protected dug wells, protected springs and rainwater provided collection time is no more than 30 minutes for
a round trip including queuing \citep{wssccWaterSanitationHygiene2014}. Also (SDGs) establishes "access" as satisfactory water to meet household needs is surely available close to home \citep{GoalCleanWater}.

@@

Improving water accessibility has been a priority by many organizations, realizing it is the basic human right to have clean and accessible drinkable water in the past 15 years. From 2006 to 2016, overall water accessibility has been improving by utilizing the indicators of the past \citep{fullerTrackingProgressGlobal2016}. However, some researchers raise concerns on lack of clarity with the global water accessibility monitoring \citep{ondaGlobalAccessSafe2012, jiaHighResolutionSpatialDistribution2016}. However, in an era of rapidly changing technologies, international and government policies, the older researches are not adequate. For an example of The eight Millennium Development Goals (MDGs) upgrading into The Sustainable Development Goals (SDGs). In light of the newest (SDGs) providing clean and accessible drinking water for all by 2030, researchers have devoted their studies to understand water accessibility at global and specific country levels. Several research and studies have focused global water accessibility ,and its progress \citep{sorensonSafeAccessSafe2011,bainAccountingWaterQuality2012,wssccWaterSanitationHygiene2014,  ondaGlobalAccessSafe2012, bartramGlobalMonitoringWater2014, ondaCountryClusteringApplied2014, whoDrinkingwater,fullerTrackingProgressGlobal2016, weiyuyuGlobalPerspectiveDrinkingwater2016, grahamAnalysisWaterCollection2016,overboOnplotDrinkingWater2016}. While there have been studies focusing on the local community in different parts of the country learning about their water accessibility and sanitation initiation \citep{jagalsDoesImprovedAccess2006, geereDomesticWaterCarrying2010, simaWaterFlowsEnergy2013, hoChallengeGlobalWater2014, sakisakaIntroductionCommunityWater2015, jiaHighResolutionSpatialDistribution2016}. Where majority raised concerns about the lack of monitoring sustainable water accessibility measurements for many people and some argue for a focus on many people's access to drinking water sources. Nonetheless, there is a lack of robust study on transportation to enhance water accessibility for all people by 2030. 

@@

The journal articles were missing what modes of transportation may enhance water accessibility. Therefore we will be analyzing the impact of transportation modes (usage/ownership) on water accessibility. We will therefore research by statistical analysis in a global scale and pilot in one of the countries to determine if the water accessibility variables predictors can improve the water accessibility for its country.
% citep (for citations fully enclosed in parentheses)
% cite (for citations without any parentheses)
% citet (for citations where the year only is in parentheses)
%\textit{Discuss the who/what/when/where? (You already have this... just need to reorganize or improve structure)}
\eject
